---
title: "HW3"
author: "Alex Filo"
date: "9/27/2021"
output: html_document
---
https://github.com/alexfilo/Week-3


```{r}
library(dplyr)


library(nycflights13)
library(ggplot2)
head(flights)
```

1. How many flights have a missing dep_time? What other variables are missing? What might these rows represent?

```{r}
missing_dep_time <- filter(flights, is.na(dep_time) == TRUE)
head(missing_dep_time)
length(missing_dep_time$dep_time)
```
These are 8255 rows that are missing a departure time. These rows are also missing values for the variables dep_delay, arr_time, arr_delay, arr_time. These rows may represent flights that were cancelled and never actually departed.


2. Currently dep_time and sched_dep_time are convenient to look at, but hard to compute with because they’re not really continuous numbers. Convert them to a more convenient representation of number of minutes since midnight.

```{r}
x <- 515
minutes <- x %% 100
(hours <- (x - minutes) / 100)
(minutes_since_midnight <- hours * 60 + minutes)

```

```{r}
mutate(flights, dep_time_minutes = dep_time %% 100, dep_time_hours = (dep_time - dep_time_minutes) / 100, dep_time_minutes_since_midnight = dep_time_hours * 60 + dep_time_minutes)

mutate(flights, sched_dep_time_minutes = sched_dep_time %% 100, sched_dep_time_hours = (sched_dep_time - sched_dep_time_minutes) / 100, sched_dep_time_minutes_since_midnight = sched_dep_time_hours * 60 + sched_dep_time_minutes)

```

3. Look at the number of canceled flights per day. Is there a pattern? Is the proportion of canceled flights related to the average delay? Use multiple dyplr operations, all on one line, concluding with ggplot(aes(x= ,y=)) + geom_point()


```{r}
library(lubridate)
flights %>% mutate(day_of_year = yday(time_hour)) %>% 
  group_by(day_of_year)%>% summarize(length(is.na(arr_delay))) %>% 
  plot(type = 'l')
```
Yes there is clearly a pattern. It seems that the number of cancelled flights per day oscillates every other day



```{r}
library(lubridate)
flights %>% 
  mutate(day_of_year = yday(time_hour)) %>% 
  group_by(day_of_year) %>% 
  summarize(
      cont = n(),
      delay = mean(arr_delay, na.rm = TRUE),
      cancelled_flights = mean(is.na(arr_delay))) %>%
  ggplot( mapping = aes(x = cancelled_flights, y = delay)) +
  geom_point()
```

Yes it does seem that the proportion of cancelled flights is related the average delay, they appear positively correlated.
